Monitoring Time Series With Missing Values:\\a Deep Probabilistic Approach

### 2022-02-16 paper.tex
related work, acknowledgements

@@

>>>>

There appear to be two interconnected areas related to this
research. One area is uncertainty representation and propagation
in recurrent neural models. The other area is handling of
missing values in time series, again in the context of
recurrent neural models in particular.

The importance of uncertainty quantification in deep learning is
well understood~\cite{MFS+21}.  Recurrent neural networks can
express forecast uncertainty through predicting distribution
parameters, such as the mean and the standard deviation, instead
of point values~\cite{HS97}. When expressing uncertainty by closed-form
distributions is insufficient, stochastic latent
variables are introduced into RNNs~\cite{YB21,CKD+15,FSK+16}. 
Uncertainty representation in RNNs is related to uncertainty
propagation and multi-step forecasting. For multi-step
forecasting, uncertainty must be propagated multiple steps into
the future. Uncertainty propagation is usually achieved through
random sampling during training or inference~\cite{LYY+19,AV20,YB21}. 
Our approach differs in that conventional RNN architectures are
leveraged to represent uncertainty in both the input and
the output, and that uncertainty propagation is accomplished
deterministically, without resorting to random sampling, which
facilitates efficient training and inference.

Handling of missing values in time series has inspired research
for decades due to the fact that many otherwise efficient and
robust algorithms, in particular those based on recurrent neural
architectures, require that all values in the time series
are present and lie within a valid range~\cite{WSY+21}. A
widespread approach is to \textit{impute} the data,
that is, to replace missing values with values inferred from
other values in the same time series or in other time series
in the data set~\cite{KC18,SYG+19}. Alternatively, a
missing value is treated as an observation itself, often by
introducing an auxiliary indicator variable~\cite{LKW16,BDS21}.
In our work, we take a third approach --- a missing value,
either due to an absent observation or in the course of
multi-step forecasting, is replaced by a parametrically
specified belief distribution of the value based on the past
observations.

@@

We thank PUB+ for providing computational facilities for
conducting the empirical evaluation. David Tolpin is partially
supported by Israel-U.S. Industrial Research and Development
Foundation's Cybersecurity technology for critical power
infrastructure AI-based centralized defense and edge resilience
project.

\nocite{BDS21}
\nocite{CPK+18}
\nocite{SYG+19}
\nocite{KC18}
\nocite{LKW16}
\nocite{BRH15}
\nocite{AV20}
\nocite{FSK+16}
\nocite{MFS+21}
\nocite{FSP+16}
\nocite{SZN+19}
\nocite{LYY+19}
\nocite{CYP+21}
\nocite{YB21}
\nocite{CKD+15}
\nocite{HS97}
\nocite{CMB+14}
\nocite{WSY+21}
